\section{Literature review} \label{sec:litrev}

In a preparation to choosing the right approach for this problem, a research on
the recent works and advances in autonomous drone racing has been conducted. A
selective literature review on the topic is given in details on
table~\ref{table:drone-racing-literature}. To select the most relevant papers related
to this thesis, whose focus is mainly on the perception and deep learning, most
papers that treated advanced control solutions were discarded. Using search
engines and keywords such as ``drone racing'', ``deep learning'', ``IROS'' and
the like, a dozen of results were found to begin the review. By looking into
the references of the most interesting papers, and mainly visiting the websites
of the research groups and authors, more interesting articles were found.

The result of this literature review is a deeper knowledge of how autonomous
drone racing is approached, and mainly what types of sensors are used to solve
this challenge efficiently. Surprisingly, only a few articles are accompanied
with the source code of the solution presented, which greatly narrows the
options to tackle the problem. The following section sums up the general
approach chosen by these papers.

\input{include/tables/literature_review.tex}

\subsection{General approach}
As it can be seen from the preceding literature review, most robotic systems'
operation can be modeled by the commonly known \emph{sense, plan, act}
paradigm:

\begin{figure}[h]
	\centering
	\begin{tikzpicture}[node distance=2cm,-latex, scale=1.6, every
		node/.style={scale=1.6}, box/.style = {draw,rectangle, minimum
		width=2cm}]
		\node[draw,rectangle] (sense) {Sense};
		\node[draw,rectangle,below of=sense,xshift=2cm] (plan) {Plan};
		\node[draw,rectangle,below of=sense,xshift=-2cm] (act) {Act};

		\draw[thick] (sense) -- (plan);
		\draw[thick] (plan) --(act);
		\draw[thick] (act) -- (sense);
	\end{tikzpicture}
	\caption{The sense, plan, act robotic paradigm.}
	\label{fig:robotic_paradigm}
\end{figure}

\begin{itemize}
	\item{\textbf{Sense}}: gather information using sensors (camera, IMU, sonar...).
	\item{\textbf{Plan}}: create a world model using all the information, and plan
		the next move.
	\item{\textbf{Act}}: carry out the actions that the plan calls for.
\end{itemize}

~\\
This thesis will be focused mainly on the sensing of the drone control, and
more precisely using deep learning and computer graphics. However, an important
part of the trajectory planning directly follows the sensing phase, therefore
those two first phases of the control loop can be included in the scope of the
project.

To this day, most drones in the robotic research field are running \emph{Robot
Operating System} (ROS),  which is a set of ``libraries and tools to help
software developers create robot applications''~\cite{ROS}. It allows to
independently run programs as ``nodes'', which can communicate with each other
using a principle of ``subscription'' and ``publication`` on easily definable
topics.

ROS makes the transition between the simulated environment and the real world
seamless, because it can be installed on most Linux systems, and adds a layer
of abstraction between the hardware and the software, by distributing packages
built by the community.\\

The implementation of the computer vision algorithms will be constrained within
ROS, and cooperate with the different control components, in an effective
modular manner.\\

As deep learning has known an exponential growth during the past decade,
computer vision applications tend to exploit the power of convolutional neural
networks more and more. Thanks to their impressive performance in specific
problem solving, CNNs are becoming the main choice for tasks such as object
detection, object segmentation, object recognition or object tracking.

In drone racing, the latest works, which are often the best performing, tend to
employ CNNs for the sensing part, or even as an all-in-one solution. It is a
reasonable choice mainly because neural networks are observed to offer
robustness and accuracy, to the cost of computational power. They can be hard
to train, given their sporadic nature, but it is often a very good alternative
to developing a custom algorithm which can take a lot of time and does not
guarantee consistent results, in different lighting conditions for instance.

On that note, the chosen method for solving the drone racing challenge is
using a convolutional neural network, coupled with a simple state-machine 
using a PID controller to steer the drone.
